Predicting Diabetes Based on Various Factors Using Machine Learning Models

### 2023-12-13 manuscript/manuscript.tex
Addition of Histograms, creation of data folder as well as upload
Decision Tree Model Performance
Decision tree structure code change
Decision Tree Results Table, elimination of old model
Confusion matrix heatmap
Changes and additions to introduction

\section{Introduction}
\label{sec:intro}
    According to the American Diabetes Association, about 11.3 percent of Americans, or about 37.3 million people, have diabetes.
    Of those 37.3 million people, about 28.7 million were actually diagnosed with diabetes, while the remaining 8.6 million were
    left undiagnosed (\citet{CDC2022Diabetes}). Those left undiagnosed are at risk for even more serious illness if left untreated. 
    Diabetes is a disease where your body does not create enough insulin, or use it properly, in order to get glucose into your cells 
    and use it for energy (\cite{NIH2023Whatis}). Therefore, it is very important that your body has a normal glucose level. In this 
    paper, I will be working to determine the pre-existing factors that can be used in order to predict if a person may have diabetes. 
    Establishing the predictors is very important to me as many of my family members have a long history of suffering from this disease. 
    It is important to better predict this disease to save people from unnecessary suffering.

@@

@@

\begin{table}[ht]
  \centering
  \caption{Confusion Matrix} 
  \begin{tabular}{rrr}
    \toprule
    & 0 & 1 \\ 
    \midrule
  0 & 318 & 47 \\ 
    1 & 53 & 136 \\ 
    \bottomrule
  \end{tabular}
  \label{tab:conf_matrix}
  \end{table}

\begin{figure}[tbp]
  \centering
  \caption{Pruned Decision Tree Structure}
  \includegraphics[width=\textwidth]{Pruned_tree.pdf}
  \label{fig:prstructure}
  \end{figure}

>>>>

\section{Introduction}
\label{sec:intro}
    According to the American Diabetes Association, about 11.3 percent of Americans, or about 37.3 million people, have diabetes.
    Of those 37.3 million people, about 28.7 million were actually diagnosed with diabetes, while the remaining 8.6 million were
    left undiagnosed (\citet{CDC2022Diabetes}). Those left undiagnosed are at risk for even more serious illness if left untreated. 
    Diabetes is a disease where your body does not create enough insulin, or use it properly, in order to get glucose into your cells 
    and use it for energy (\cite{NIH2023Whatis}).

    There are two types of diabetes that the majority of the patients have, type 1 or 2. The bodies of people that have type 1 diabetes
    completely do not make insulin, so they must take a daily insulin shot. Whereas in type 2 diabetes, these patients produce insulin but 
    their bodies do not use it properly (\cite{JDC2023Difference}).

    Therefore, it is very important that your body has a normal glucose level. In this 
    paper, I will be working to determine the pre-existing factors that can be used in order to predict if a person may have diabetes. 
    Establishing the predictors is very important to me as many of my family members have a long history of suffering from this disease. 
    It is important to better predict this disease to save people from unnecessary suffering.

@@

  \begin{figure}[tbp]
    \centering
    \caption{Each variable represented as a histogram}
      \includegraphics[width=\textwidth]{Histograms.pdf}
      \label{fig:histogram}
      \end{figure}

@@

\begin{table}[ht]
    \centering
    \caption{Decision Tree Results}
    \label{tab:dtr} 
    \begin{tabular}{rrr}
      \toprule
      Metric & Value\\
      \midrule
      Accuracy & 0.82\\
      Precision & 0.72\\
      Recall & 0.74\\
      F1 Score & 0.73\\
      \bottomrule
      \end{tabular}
    \end{table}

  \begin{figure}[tbp]
      \centering
      \caption{Confusion Matrix Heatmap}
      \includegraphics[width=\textwidth]{Confusion Matrix Heatmap}
      \label{fig:Heatmap}
      \end{figure}
